Online Multiclass Linear Classification with Bandit Feedback

### 2018-12-20 arxiv-version/main.tex
Add mappings and kernels

TODO: Mappings and kernels!

>>>>

We construct the three different mappings $\phi_n, \psi_n, \rho$. The first two
are parametrized by a non-negative integer $n$. The domain of $\phi_n$ and
$\psi_n$ is $\R^d$. The domain of $\rho$ is the unit ball of $\R^d$. The
co-domain for $\phi_n$ and $\psi_n$ is $\R^p$ where $p = \sum_{i=0}^n
\binom{i+d-1}{d-1}$ equipped with the standard inner product $\ip{x}{x'} =
\sum_{i=1}^p x_i x'_i$. The co-domain is the classical separable Hilbert space
$\ell_2 = \{ x \in \R^\infty ~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped
with the standard inner product $\ip{x}{x'} = \sum_{i=1}^\infty x_i x'_i$. We
index the coordinates of the co-domain $\R^p$ by $d$-tuples $(\alpha_1,
\alpha_2, \dots, \alpha_d)$ of non-negative integers such that $\alpha_1 +
\alpha_2 + \dots + \alpha_d \le n$. Similarly, we index the coordinates of
$\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
integers. The mappings are defined by
\begin{align*}
\left(\phi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
& = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
\\
\left(\psi_n(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
& = \sqrt{\binom{n}{\alpha_1 + \alpha_2 + \dots + \alpha_d} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
\\
\left(\rho(x)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)}
& = \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
\end{align*}
where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
is the multinomial coefficient and $\binom{n}{k} = \frac{n!}{(n-k)!k!}$ is the binomial coefficient.

Mappings $\psi_n$ and $\rho$ have simple-to-compute kernels
\begin{align*}
K_{\psi_n}(x,x') & = \ip{\psi_n(x)}{\psi_n(x')}_{\R^p} = \left( 1 + \ip{x}{x'} \right)^n \; , \\
K_{\rho}(x,x') & = \ip{\rho(x)}{\rho(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}} \; .
\end{align*}
In passing we note that the formula for $K_\rho$ implies the mapping $\rho$ is
well defined. Indeed, since $K_{\rho}(x,x) < +\infty$ for any $x$ in the unit
ball of $\R^d$, it means that $\rho(x)$ indeed lies in $\ell_2$.
